\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=2cm]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{parskip}

\definecolor{accent}{HTML}{2563EB}
\definecolor{lightgray}{HTML}{F3F4F6}

\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    urlcolor=accent,
}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

\title{\textbf{Dashboard Columns Reference}\\[0.3em]
\large All columns surfaced in \texttt{dashboard/data.py}}
\author{Ingestion Pipeline Reports}
\date{\today}

\begin{document}

%% ============================================================
\section{Model Export Columns (\texttt{MODEL\_EXPORT\_COLUMNS})}
\label{sec:model-export}
%% ============================================================

These columns are \textbf{computed} in \texttt{\_build\_model\_export\_df} by merging data from three formatting steps (\texttt{extract\_model\_inputs}, \texttt{extract\_model\_methodology}, \texttt{extract\_model\_assumptions}) plus \texttt{bronze\_mapping}. They appear in the CSV export and the Model Export dashboard page.

\begin{longtable}{@{} L{2.8cm} L{2.2cm} L{3.2cm} L{2.2cm} L{2.5cm} L{3cm} @{}}
\toprule
\textbf{Column} & \textbf{Source} & \textbf{Description} & \textbf{Type} & \textbf{Example} & \textbf{Utility} \\
\midrule
\endfirsthead
\toprule
\textbf{Column} & \textbf{Source} & \textbf{Description} & \textbf{Type} & \textbf{Example} & \textbf{Utility} \\
\midrule
\endhead
\bottomrule
\endfoot

\texttt{document\_ name}
  & \texttt{bronze\_ mapping}
  & Human-readable PDF filename.
  & \texttt{str}
  & \texttt{"JPMorgan\_ 20240315.pdf"}
  & Row label so consumers know which report the data came from. \\
\midrule

\texttt{model\_name}
  & inputs
  & Exact model name or label used in the report for the equity return forecast approach.
  & \texttt{str}
  & \texttt{"Building Blocks"}
  & Identifies the forecasting methodology by its report-native name. \\
\midrule

\texttt{notes\_model}
  & inputs
  & Optional short keywords summarizing the approach.
  & \texttt{str}
  & \texttt{"DDM, macro overlay"}
  & Quick at-a-glance characterization. \\
\midrule

\texttt{variables}
  & inputs
  & Comma-separated list of primary input variables. Serialized from a JSON array.
  & \texttt{str}
  & \texttt{"earnings growth, dividend yield, P/E ratio"}
  & Enumerates what the model consumes for cross-institution comparison. \\
\midrule

\texttt{variables\_nb}
  & computed
  & Count of items in the \texttt{variables} array.
  & \texttt{int}
  & \texttt{7}
  & Quick complexity proxy. \\
\midrule

\texttt{steps\_summary}
  & methodology
  & Concise narrative of the end-to-end equity forecast approach.
  & \texttt{str}
  & \texttt{"Decomposes returns into dividend yield, earnings growth\ldots"}
  & One-paragraph overview for comparison tables. \\
\midrule

\texttt{steps\_detailed}
  & methodology
  & Detailed narrative including all stated assumptions, constraints, and conditions.
  & \texttt{str} (multi-para.)
  & \emph{(long text)}
  & Full audit trail for deep-dive analysis. \\
\midrule

\texttt{variables\_ importants}
  & inputs
  & Comma-separated list of variables the report flags as important.
  & \texttt{str}
  & \texttt{"earnings growth, valuation"}
  & Highlights which inputs the institution considers most influential. \\
\midrule

\texttt{assumptions\_ values}
  & inputs
  & Bullet-pointed value-type assumptions (numbers, macro climate). Implied ones tagged \texttt{(implied)}.
  & \texttt{str} (bullets)
  & \texttt{"* Inflation = 2.5\%\textbackslash n* GDP growth = 2\%"}
  & Captures numeric assumptions baked into the forecast inputs. \\
\midrule

\texttt{assumptions\_ structural}
  & methodology
  & Bullet-pointed structural assumptions (variable relationships, functional forms).
  & \texttt{str} (bullets)
  & \texttt{"* Returns decompose additively"}
  & Captures methodological assumptions about how inputs interact. \\
\midrule

\texttt{uses\_ regressions}
  & methodology
  & Whether the model uses regression techniques.
  & \texttt{int}: 0 or 1
  & \texttt{1}
  & Binary tag for cross-institution technique comparison. \\
\midrule

\texttt{uses\_ simulations}
  & methodology
  & Whether the model uses simulation techniques (Monte Carlo, scenario, stochastic).
  & \texttt{int}: 0 or 1
  & \texttt{0}
  & Binary tag for technique comparison. \\
\midrule

\texttt{uses\_averages}
  & methodology
  & Whether the model uses historical / long-run / equilibrium averages as inputs.
  & \texttt{int}: 0 or 1
  & \texttt{1}
  & Binary tag for technique comparison. \\
\midrule

\texttt{uses\_mean\_ reversion}
  & methodology
  & Whether the model assumes mean reversion of any variable.
  & \texttt{int}: 0 or 1
  & \texttt{1}
  & Binary tag for technique comparison. \\
\midrule

\texttt{assumptions\_ classified}
  & assumptions
  & Bullet-pointed assumptions, each tagged with a classification and building block.
  & \texttt{str} (bullets)
  & \texttt{"* [mean-reversion] P/E reverts to long-run avg (re: valuation)"}
  & Unified classified view for systematic comparison. \\
\midrule

\texttt{techniques\_ used}
  & assumptions
  & Comma-separated list of analytical techniques found in the report, each with its complexity score. Serialized from an array of \texttt{\{technique\_name, complexity\}} objects.
  & \texttt{str}
  & \texttt{"DDM (7), Monte Carlo (8), historical avg (2)"}
  & Enumerates specific techniques for cross-institution comparison. \\
\midrule

\texttt{sophistication\_ index}
  & assumptions
  & Overall 1--10 score reflecting the methodological sophistication of the model, grounded in a 5-tier reference scale (1--2 simple averages, 3--4 regression/decomposition, 5--6 multi-factor/scenario, 7--8 simulation/Bayesian, 9--10 DSGE/ML).
  & \texttt{int} in $[1, 10]$
  & \texttt{6}
  & Single numeric score for ranking and comparing model complexity across institutions. \\
\midrule

\texttt{sophistication\_ explanation}
  & assumptions
  & Brief justification (1--3 sentences) for the assigned sophistication score.
  & \texttt{str}
  & \texttt{"Uses multi-factor decomposition with scenario overlays\ldots"}
  & Audit trail so researchers can verify the sophistication rating. \\

\end{longtable}


\end{document}
